Timeseries Example

### 2015-10-22 timeseries/timeseries_example.Rmd
Updated interval_prob to give an option for closed or open intervals, and include NA arguments for one element of t.range, to make one-sided tests (rather than inside range).

source('prepare_data.R')
source('climate_model.R')
```
```{r load_data, echo=T, eval=T, cache=T, dependson=c('setup')}
data <- prepare_climate_data('rcp 4.5')

@@

predictions <- data.frame(true.model = c('log CO2', 'log CO2', 'Slow TSI', 'Slow TSI'),
                          trader.model = rep_len(c('log CO2', 'Slow TSI'), 4),
                          prob = c(
                            interval_prob(trader.co2.true.co2, n_horizon = trader_horizon, t.range = c(low, high)),
                            interval_prob(trader.tsi.true.co2, n_horizon = trader_horizon, t.range = c(low, high)),
                            interval_prob(trader.co2.true.tsi, n_horizon = trader_horizon, t.range = c(low, high)),
                            interval_prob(trader.tsi.true.tsi, n_horizon = trader_horizon, t.range = c(low, high))
                          )
)

@@

| Trader's Model | True model = $\log\COO$ | True model = Slow TSI |
|:---------------|------------------------:|------------------:|
| $\log\COO$     | `r round(predictions$prob[predictions$true.model == 'log CO2' & predictions$trader.model == 'log CO2'],3)` | `r round(predictions$prob[predictions$true.model == 'Slow TSI' & predictions$trader.model == 'log CO2'],3)` |
| Slow TSI     | `r round(predictions$prob[predictions$true.model == 'log CO2' & predictions$trader.model == 'Slow TSI'],3)` | `r round(predictions$prob[predictions$true.model == 'Slow TSI' & predictions$trader.model == 'Slow TSI'],3)` |

>>>>

source('prepare_data.R')
source('climate_model.R')

prt <- function(x,digits,flag='',mark='') {
  formatC(x, digits=digits, format='f', flag=flag, big.mark=mark)
}
```
```{r load_data, echo=T, eval=T, cache=T}
data <- prepare_climate_data('rcp 4.5')

@@

predictions <- data.frame(true.model = c('log CO2', 'log CO2', 'Slow TSI', 'Slow TSI'),
                          trader.model = rep_len(c('log CO2', 'Slow TSI'), 4),
                          prob = c(
                            interval_prob(trader.co2.true.co2, n_horizon = trader_horizon, t.range = c(low, high), TRUE),
                            interval_prob(trader.tsi.true.co2, n_horizon = trader_horizon, t.range = c(low, high), TRUE),
                            interval_prob(trader.co2.true.tsi, n_horizon = trader_horizon, t.range = c(low, high), TRUE),
                            interval_prob(trader.tsi.true.tsi, n_horizon = trader_horizon, t.range = c(low, high), TRUE)
                          )
)

@@

| Trader's Model | True model = $\log\COO$ | True model = Slow TSI |
|:---------------|------------------------:|------------------:|
| $\log\COO$     | `r prt(predictions$prob[predictions$true.model == 'log CO2' & predictions$trader.model == 'log CO2'],3)` | `r prt(predictions$prob[predictions$true.model == 'Slow TSI' & predictions$trader.model == 'log CO2'],3)` |
| Slow TSI     | `r prt(predictions$prob[predictions$true.model == 'log CO2' & predictions$trader.model == 'Slow TSI'],3)` | `r prt(predictions$prob[predictions$true.model == 'Slow TSI' & predictions$trader.model == 'Slow TSI'],3)` |
